---
title: Checking Installation
author: 'Jon Jaeger'
date: '2022-03-01'
categories: ["R","Python"]
tags: ["ggplot", "matplotlib"]
hero: /images/hero-3.jpg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This post will check the package installation and integration of my site with R and Python. Verification of these steps is necessary to ensure that everything is installed properly.

# Check the R library installation

First, load the library ggplot from the [tidyverse](https://tidyverse.tidyverse.org).

```{r}
library(ggplot2)
```

Next, plot a sine wave and label the axes.

```{r}
# define the range of the angle to be zero to 2*pi
theta <- seq( 0, 2*pi, by = 2*pi/(100 - 1 ) )

# make a data frame that contains both angle and the sine of the angle
df <- data.frame( 't' = theta, 'sine' = sin(theta) )

# generate a plot and labels
p <- ggplot( data=df, aes( x=t, y=sine ) ) +
    geom_line() + theme_classic()
# add some plot labels
p <- p + xlab( expression( paste( theta, ' (rad)' ) ) )
p <- p + ylab( expression( sin(theta) ) )
p <- p + ggtitle( 'Sine Function versus Angle' ) + theme(plot.title = element_text(hjust = 0.5))
print(p)
```

There is the plot that we wanted.

# Check the Python installation

```{r, include=FALSE, echo=TRUE}
library(reticulate)
```

First, import matplotlib and numpy

```{python}
import numpy as np

import matplotlib as mpl
import matplotlib.pyplot as plt
```
Next, plot a sine wave and label the axes.

```{python}
theta = np.linspace( 0, 2*np.pi, 100 )
y = np.sin( theta )
plt.figure()
plt.plot( theta, y, 'k' )
plt.xlabel( r'$\theta\ (rad)$' )
plt.ylabel( r'$sin(\theta)$' )
plt.title( 'Sine Function versus Angle' )
plt.show()
```


We see that the plot from ggplot is very similar to the one generated using matplotlib.
